Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2015-04-09 Paper.tex
ethash I - block header validity

The nonce, $H_n$, must satisfy the relation:
\begin{equation}
%\mathtt{PoW}(H, H_n) \dfrac{\leqslant}{den} \frac{2^{256}}{H_d}
\mathtt{PoW}(H, H_n) \leqslant \frac{2^{256}}{H_d}
\end{equation}

Where $\mathtt{PoW}$ is the proof-of-work function (see section \ref{ch:pow}): this evaluates to an pseudo-random number cryptographically dependent on the parameters $H$ and $H_n$. Given an approximately uniform distribution in the range $[0, 2^{256})$, the expected time to find a solution is proportional to the difficulty, $H_d$.

@@

Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv & \mathtt{PoW}(H, H_n) \leqslant \frac{2^{256}}{H_d} \quad \wedge \\
& & H_d = D(H) \quad \wedge \\
& & H_g \le H_l  \quad \wedge \\
& & H_l < {P(H)_H}_l + \lfloor\frac{{P(H)_H}_l}{1024}\rfloor  \quad \wedge \\
& & H_l > {P(H)_H}_l - \lfloor\frac{{P(H)_H}_l}{1024}\rfloor  \quad \wedge \\
& & H_l \geqslant 125000  \quad \wedge \\
& & H_s > {P(H)_H}_s \quad \wedge \\
& & H_i = {P(H)_H}_i +1 \quad \wedge \\
& & \lVert H_x \rVert \le 1024
\end{eqnarray}

>>>>

The nonce, $H_n$, must satisfy the relation:
\begin{equation}
\mathtt{PoW}(H, H_n, \mathbf{d})[0] = H_m \quad \wedge \quad \mathtt{PoW}(H, H_n, \mathbf{d})[1] \leqslant \frac{2^{256}}{H_d}
\end{equation}

With $\mathbf{d}$ being the current DAG, a large data set needed to compute the mixHash, and $\mathtt{PoW}$ is the proof-of-work function (see section \ref{ch:pow}): this evaluates to an array with the first item being the mixHash, to proof that a correct DAG has been used, and the second item being a pseudo-random number cryptographically dependent on $H$ and $\mathbf{d}$. Given an approximately uniform distribution in the range $[0, 2^{256})$, the expected time to find a solution is proportional to the difficulty, $H_d$.

@@

Thus we are able to define the block header validity function $V(H)$:
\begin{eqnarray}
V(H) & \equiv & \mathtt{PoW}(H, H_n, \mathbf{d})[0] = H_m \quad \wedge \\
& & \mathtt{PoW}(H, H_n, \mathbf{d})[1] \leqslant \frac{2^{256}}{H_d} \quad \wedge \\
& & H_d = D(H) \quad \wedge \\
& & H_g \le H_l  \quad \wedge \\
& & H_l < {P(H)_H}_l + \lfloor\frac{{P(H)_H}_l}{1024}\rfloor  \quad \wedge \\
& & H_l > {P(H)_H}_l - \lfloor\frac{{P(H)_H}_l}{1024}\rfloor  \quad \wedge \\
& & H_l \geqslant 125000  \quad \wedge \\
& & H_s > {P(H)_H}_s \quad \wedge \\
& & H_i = {P(H)_H}_i +1 \quad \wedge \\
& & \lVert H_x \rVert \le 1024
\end{eqnarray}
